Ornaments as indicators of social changes in northeastern Taiwan before and after European colonial period

### 2019-12-16 analysis/paper/paper.Rmd
solved the knitting and ploting issue

```{r plot-altogether, fig.cap= "Frequency of ornament subtypes showing the changes in frequency across time periods for metal rings, carnelian beads, bells, and glass beads", eval = TRUE}
library(cowplot)
plot_multi_types_by_period <- 
plot_grid(ring_shape_plot,
          agate_bead_shape_plot, 
          bell_shape_plot, 
          glass_bead_plot,
          ncol=1,
          align = "h",
          axis = "lr",
          rel_widths = 1,
          rel_heights = c(1,1,0.7,0.62))
ggsave(plot = plot_multi_types_by_period,
       here("analysis", "figures",
       "plot-multi-types-by-period.jpg"),
       width = 135, 
       dpi = 300,
       height = 95,
       units = "mm")
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-multi-types-by-period.jpg"))
```

>>>>

```{r plot-altogether, fig.cap= "Frequency of ornament subtypes showing the changes in frequency across time periods for metal rings, carnelian beads, bells, and glass beads"}
library(cowplot)
plot_multi_types_by_period <- 
plot_grid(ring_shape_plot,
          agate_bead_shape_plot, 
          bell_shape_plot, 
          glass_bead_plot,
          ncol=1,
          align = "h",
          axis = "lr",
          rel_widths = 1,
          rel_heights = c(1,1,0.7,0.62))
ggsave(plot = plot_multi_types_by_period,
       here("analysis", "figures",
       "plot-multi-types-by-period.jpg"),
       width = 135, 
       dpi = 300,
       height = 95,
       units = "mm")
knitr::include_graphics(here("analysis", 
                             "figures", 
                             "plot-multi-types-by-period.jpg"))
```
